---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oulad

Data loaders for the **Open University Learning Analytics Dataset
(OULAD)**, packaged for convenient use in R.

This package provides a reproducible structure for working with the
seven core OULAD tables in efficient Parquet format, along with helper
functions for loading and filtering them.

## Installation

``` r
# Install from GitHub
# (requires remotes or devtools)
remotes::install_github("data-edu/oulad")

# Load the package
library(oulad)
```

## Data Overview

This package mirrors the original OULAD tables:

| Function                        | Description                                                   |
|-----------------------|-----------------------------|
| `oulad::assessments()`         | Assessment structure and key dates                            |
| `oulad::courses()`             | Module and presentation metadata                              |
| `oulad::studentAssessment()`   | Student submissions and assessment results                    |
| `oulad::studentInfo()`         | Demographics, age band, region, etc.                          |
| `oulad::studentRegistration()` | Student module registration records                           |
| `oulad::vle()`                 | Virtual Learning Environment (VLE) materials and release info |
| `oulad::studentVle()`          | **Large** log of student interactions with VLE materials      |

## How to Load the Data

```{r}
library(oulad)

assessments <- oulad::assessments()
courses <- oulad::courses()
student_assess <- oulad::studentAssessment()
student_info <- oulad::studentInfo()
student_reg <- oulad::studentRegistration()
vle <- oulad::vle()
student_vle <- oulad::studentVle()
```

## How to Join the Data

``` r
library(oulad) 
library(dplyr)

students <- student_info %>% 
    left_join(courses) %>% 
    left_join(student_reg)

assessments <- student_assess %>% 
    left_join(assessments)

interactions <- student_vle %>%
    left_join(vle) %>%
    left_join(courses)
```

## Developers

The raw OULAD CSV files are **not distributed** with this package
because of their size.\
To rebuild the Parquet files locally, first download the dataset from
the official OULAD site:

> **Download source:**\
> <https://analyse.kmi.open.ac.uk/open-dataset>

Then, place the CSVs under `data-raw/csv/` and run:

``` r
source("data-raw/make-extdata.R")
```

This script will convert the CSVs into compressed Parquet files under
`inst/extdata/` for fast access in R.\
These files are ignored by version control (see `.Rbuildignore`).

## Authors

-   **Joshua M. Rosenberg** – University of Tennessee, Knoxville\
-   **Kelly L. Boles** – University of Tennessee, Knoxville

## License & Citation

Data © The Open University, used under the terms of the [OULAD
license](https://analyse.kmi.open.ac.uk/open-dataset).

If you use this package or the data in research or teaching, please
cite:

> Kuzilek, J., Hlosta, M., & Zdrahal, Z. (2017).\
> *Open University Learning Analytics Dataset (OULAD).*\
> *Scientific Data*, 4, 170171.\
> <https://doi.org/10.1038/sdata.2017.171>

and

> Rosenberg, J. M., & Boles, K.L. (2025).\
> *oulad: Load and use the Open University Learning Analytics Dataset
> (OULAD).*\
> GitHub repository: <https://github.com/data-edu/oulad>
